% Paste-ready measurement protocol for the Experimental Setup subsection.

\textbf{PCIe Bandwidth and Energy Measurement.}
We measure host-to-device PCIe bandwidth with a pinned-memory CUDA copy
microbenchmark rather than using the nominal link rate. For each platform, we
allocate a page-locked FP16 host buffer and a GPU buffer with the same size as
one expert shard, issue repeated non-blocking H2D copies, synchronize the
device before and after the measurement window, and compute effective bandwidth
as transferred bytes divided by elapsed time. We use this measured bandwidth to
calibrate the copy/compute overlap window and validate the PCIe activity
reported in the controlled experiments; Nsight Systems traces are additionally
collected for representative Naive, Pre-gated, and SPICE runs to confirm
whether H2D copies appear on the critical path or overlap with target
computation.

Energy results are reported as GPU energy telemetry, not full-system energy. We
sample GPU power through NVML (via
\texttt{nvidia-smi --query-gpu=power.draw}) at 100--200\,ms intervals during
paired replay runs on the same GPU. For each policy, replay traffic is
generated from the measured number of expert transfers and the same compute
kernel configuration, and energy is estimated as average sampled GPU power
multiplied by replay elapsed time; energy per token is then divided by the
number of replayed decoding steps. We do not use RAPL in this study and
therefore do not claim CPU package or whole-system energy. The energy table
should be interpreted as GPU-side replay telemetry that complements latency and
PCIe measurements.
